\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor} % for color definitions
\usepackage{mdframed} % for framing and shading the problems
\usepackage{lipsum} % for generating text, remove in your actual document
\usepackage{geometry} % for page layout
\usepackage{titling} % for title page layout

% Set the page size and margins
\geometry{letterpaper, portrait, margin=1in}

% Define a new environment for the problems that takes one argument for the problem number
\newenvironment{problem}[1]{
    \begin{mdframed}[backgroundcolor=gray!20, skipabove=\baselineskip, skipbelow=\baselineskip, nobreak=true, innerleftmargin=10pt, innerrightmargin=10pt, innertopmargin=10pt, innerbottommargin=10pt]
    \textbf{Problem #1.}
}{
    \end{mdframed}
}

% Define a new environment for the proofs
\newenvironment{proof}{
    \begin{mdframed}[nobreak=true, innerleftmargin=10pt, innerrightmargin=10pt, innertopmargin=10pt, innerbottommargin=10pt]
    \textbf{Proof.}
}{
    \hfill $\square$
    \end{mdframed}
}

% Remove section numbering
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Remove table of contents numbering
\renewcommand{\thesection}{}

% Title page info
\title{Coding Project Ideas \\ \large Capstone: The Art of Approximation}
\author{Ojas Chaturvedi}
\date{November 9, 2023}

% ------------------------------------------------------------------------------
\begin{document}

% Title page
\begin{titlingpage}
    \maketitle
    \tableofcontents
\end{titlingpage}

% ------------------------------------------------------------------------------

\section{Idea 1: Autonomous Drone Traffic Management System}
    \textbf{Purpose:} Develop a system to manage the traffic of autonomous drones in urban areas to ensure safety, efficiency, and compliance with regulations. \\ \\
    \textbf{Member 1: System Architect}
        \begin{itemize}
            \item Design the overall system architecture, including drone communication protocols and air traffic control algorithms.
            \item Ensure system scalability for handling thousands of drones simultaneously.
            \item Lead the integration of subsystems developed by other team members.
        \end{itemize}
    \textbf{Member 2: AI Specialist}
        \begin{itemize}
            \item Develop machine learning models for collision avoidance and optimal path planning.
            \item Train models using simulations and real-world data.
            \item Implement real-time decision-making algorithms for dynamic environments.
        \end{itemize}
    \textbf{Member 3: Communications Engineer}
        \begin{itemize}
            \item Establish secure and reliable communication channels between drones and the control system.
            \item Develop protocols for emergency handling and drone identification.
            \item Optimize network for low latency and high throughput.
        \end{itemize}
    \textbf{Member 4: Regulatory and Compliance Officer}
        \begin{itemize}
            \item Ensure the system complies with aviation and local government regulations.
            \item Develop a framework for privacy and data protection.
            \item Liaise with regulatory bodies and participate in the development of new regulations.
        \end{itemize}

\newpage \section{Idea 2: AI-Based Precision Medicine Platform}
    \textbf{Purpose:} Build an AI-powered platform that can analyze genetic data, medical records, and research to provide personalized treatment recommendations. \\ \\
    \textbf{Member 1: Bioinformatics Scientist}
        \begin{itemize}
            \item Develop algorithms for processing and analyzing large genomic datasets.
            \item Work on integrating genetic data with patient electronic health records (EHR).
            \item Lead the research on disease markers and drug response prediction.
        \end{itemize}
    \textbf{Member 2: Machine Learning Engineer}
        \begin{itemize}
            \item Build predictive models for disease risk and treatment outcomes.
            \item Implement natural language processing to extract insights from medical literature.
            \item Ensure the interpretability and fairness of AI models.
        \end{itemize}
    \textbf{Member 3: Data Security Expert}
        \begin{itemize}
            \item Design a secure infrastructure to protect sensitive health data.
            \item Ensure compliance with HIPAA and other health data protection regulations.
            \item Implement robust access controls and audit trails.
        \end{itemize}
    \textbf{Member 4: Clinical Specialist and User Experience Designer}
        \begin{itemize}
            \item Provide clinical expertise to guide the platform's development.
            \item Design the user interface for clinicians and patients, focusing on usability.
            \item Facilitate clinical trials and collect user feedback for continuous improvement.
        \end{itemize}

\newpage \section{Idea 3: Smart City Infrastructure and Services Integration Platform}
    \textbf{Purpose:} Develop a centralized platform that integrates various smart city services like traffic management, waste management, energy usage, and emergency services for improved efficiency and citizen experience. \\ \\
    \textbf{Member 1: Urban Planner and System Integration Specialist}
        \begin{itemize}
            \item Lead the design of the platform's architecture to integrate with existing city infrastructure.
            \item Coordinate with city officials and urban planners to ensure the platform meets the needs of the city.
            \item Oversee the integration of IoT devices and sensors across the city.
        \end{itemize}
    \textbf{Member 2: Data Scientist and Analyst}
        \begin{itemize}
            \item Analyze data from city services to find optimization opportunities.
            \item Develop predictive models for service demand and resource allocation.
            \item Implement analytics dashboards for city officials to monitor and manage services.
        \end{itemize}
    \textbf{Member 3: Data Security Expert}
        \begin{itemize}
            \item Design and maintain the network of IoT devices and sensors.
            \item Ensure reliable data collection and transmission.
            \item Implement security measures to protect the network from cyber threats.
        \end{itemize}
    \textbf{Member 4: Clinical Specialist and User Experience Designer}
        \begin{itemize}
            \item Create a user-friendly interface for citizens to interact with city services.
            \item Develop mobile and web applications for service requests, information dissemination, and feedback.
            \item Conduct user testing to refine the platform's usability.
        \end{itemize}

\newpage \section{Idea 4: Ocean Cleanup and Monitoring Autonomous Fleet}
    \textbf{Purpose:} Design and program an autonomous fleet of vessels and drones to clean up ocean waste and monitor marine health. \\ \\
    \textbf{Member 1: Marine Robotics Engineer}
        \begin{itemize}
            \item Design the autonomous navigation system for the vessels and underwater drones.
            \item Develop the control algorithms for waste collection and data gathering.
            \item Oversee the deployment and maintenance of the robotic fleet.
        \end{itemize}
    \textbf{Member 2: Environmental Data Scientist}
        \begin{itemize}
            \item Process and analyze data collected by the fleet to track pollution levels and marine biodiversity.
            \item Develop models to predict the movement of waste patches and the impact of cleanup efforts.
            \item Collaborate with environmental organizations to align efforts with conservation goals.
        \end{itemize}
    \textbf{Member 3: Software and AI Engineer}
        \begin{itemize}
            \item Implement machine learning algorithms for image recognition to identify different types of waste.
            \item Develop the AI for real-time decision making in dynamic ocean conditions.
            \item Integrate AI with robotic systems for efficient cleanup operations.
        \end{itemize}
    \textbf{Member 4: Communications and Outreach Coordinator}
        \begin{itemize}
            \item Develop a platform for sharing real-time data and insights with the public and research institutions.
            \item Coordinate with global environmental agencies to maximize the impact of the cleanup operations.
            \item Handle media relations and build educational campaigns about ocean health.
        \end{itemize}

% ------------------------------------------------------------------------------
\end{document}
% ------------------------------------------------------------------------------